Assesing Health Care Coverage and Access Utilizing the National Health Interview Survey

### 2017-03-08 paper/paper.tex

@@

@@

@@

>>>>

Because the dataset was so large, it was difficult to manage and
processing the data was time-consuming. In order to fully combat this,
we used the dplyr package in order to modify the dataset we would be
using in such a way that only incorporated the columns we needed to
address the question at hand. After, we then filtered the data so that
we would have only the information we needed to answer the questions,
while weeding out ``empty'' data such as ``not ascertained,'' ``didn't
know,'' as well as ``refused.'' When we were certain of the dataset we
needed that only contained relevant information to our questions, we
then utilized the ggplot2 R package in order to create well-labeled
graphs that visually summarized our results. From the graphs, we were
able to draw reasonable conclusions and generate an analysis of why the
data was shaped in the particular way it was.

@@

In respects to the National Health Interview Survey, we wanted to
research what percentage of the population had healthcare coverage. We
used the ``NOTCOV'' column of the survey to retrieve the amount of
individuals that had coverage and those who did not have healthcare
coverage. We do want to mention that there was a total of 1102
individual that responded with ``Don't know''. WE made the decision to
exclude these individuals from our data since they do not represent your
targeted population.

When comparing just the proportions of those who had healthcare coverage
to those who lacked coverage, there was a clear transformation. Only
10.23\% of the individuals that participated in this survey did not have
healthcare coverage. While 89.76\% of these individuals did have
coverage.

@@

\includegraphics{paper_files/figure-latex/hi2015-1.pdf}

\textbf{Figure 5. Percentage of the Respondents that Has Healthcare
Coverage}

\includegraphics{paper_files/figure-latex/hi2015employer-1.pdf}
\textbf{Figure 6. Percentage of the Respondents that Has Healthcare
Coverage}

@@

A huge discussions these recent weeks has been Obama care. Some view it
was a total disaster while others suggest that it works but it is not
perfect. Our president has spoken that this plan is terrible and this
inspired us to consider the what a reality would be like if there was no
more Obama care. As a group we believed that without government help,
individuals would have to resort to other sorts of health care plans. We
decided to focus on employers to study if there is any significant
correlation between employers and health care coverage. We do have to
note that this information lacked the participation from 42728
individuals. This number was subtracted from the group that did
responded as we were interested in the population that did have some
sort of coverage.

As our prior graph indicates, about 89.76\% of the surveyed population
expressed some sort of healthcare coverage. Out of this population we
calculated that 78.69\% of population that has some sort of healthcare
coverage attains it through an employer. This is only about a 11.07\%
difference suggesting that the way more people get their healthcare
coverage through their workforce. However we did not count those
individuals who obtained coverage through their own self-employed
business, a union, or even those who were uncertain about their
response.

After analyzing these findings, it is our suggestion that there is some
relationship between employers and a person's' health care coverage. But
must point out that it is not very clear to understand how strong this
correlation is or to even identify in what specific ways these aspects
have an influence on each other. The 11\% difference does portray the
idea that everyone is obtaining healthcare coverage from their
employers. But it is crucial to realize that the portion that missed
this question represents, in quantity, consists of more than half the
population that did decide to answer. This great lack of representation
from the population is too big to consider a strong and clear
correlation between employers and health care coverage.
